\mireval{}

### 2014-05-07 paper/paper.tex
Can't change title or abstract

% ------
\title{\mireval{}: A Transparent Codebase for Evaluating MIR}

@@

\begin{document}
%
\maketitle
%
\begin{abstract}
Central to the field of MIR research is the evaluation of algorithms used to extract information from music data.
We present \mireval{}, an open source software library which provides a transparent and easy-to-use implementation of the most common metrics used to measure the performance of MIR algorithms.
In this paper, we enumerate the metrics implemented by \mireval{} and quantitatively compare each to  existing implementations.
When the scores reported by \mireval{} differ substantially from the reference, we diagnose the differences in implementation.
We also provide a brief overview of \mireval{}'s architecture, design, and intended use.
\end{abstract}
%
\section{Evaluating MIR Algorithms}

>>>>

% ------
\title{\mireval{}}

@@

\begin{document}
%
\maketitle
%
\begin{abstract}
Central to the field of MIR research is the evaluation of algorithms used to extract information from music data.
We present \mireval{}, an open source software library which provides a transparent and easy-to-use implementation of the most common metrics used to measure the performance of MIR algorithms.
In the present work, we enumerate the metrics implemented by \mireval{} and quantitatively compare each to an existing implementation.
When the score reported by \mireval{} differs substantially from the reference, we detail the differences in implementation.
We also provide a brief overview of \mireval{}'s architecture, design, and intended use.
\end{abstract}
%
\section{Evaluating MIR Algorithms}
